The Astropy Project: Building an inclusive, open science project and status of the v2.0 software

### 2018-01-05 main.tex
word order
add missing word, build->built

Models are defined by their parameters and initialized by providing values for them. The
names of the parameters are stored in a list, \texttt{Model.param\_names}. Parameters are complex objects.
They store additional information -- default value, default unit, and parameter constraints. Parameter
values and constraints can be updated by assignment. Supported constraints include \texttt{fixed},
and \texttt{tied} parameters, and \texttt{bounds} on parameter values. The framework supports also models
for which the number of parameters and their names are defined by another argument.
A typical example is a polynomial model defined by its degree.
A model is evaluated by calling it as a function.

@@

\subsubsection{Creating New Models}
If arithmetic combinations of existing models is not sufficient, new model classes can be defined in different ways. The \package{astropy.modeling} provides tools to turn a simple function into a full-featured model, but it also allows extending the build-in model class with arbitrary code.

>>>>

Models are defined by their parameters and initialized by providing values for them. The
names of the parameters are stored in a list, \texttt{Model.param\_names}. Parameters are complex objects.
They store additional information -- default value, default unit, and parameter constraints. Parameter
values and constraints can be updated by assignment. Supported constraints include \texttt{fixed},
and \texttt{tied} parameters, and \texttt{bounds} on parameter values. The framework also supports models
for which the number of parameters and their names are defined by another argument.
A typical example is a polynomial model defined by its degree.
A model is evaluated by calling it as a function.

@@

\subsubsection{Creating New Models}
If arithmetic combinations of existing models is not sufficient, new model
classes can be defined in different ways. The \package{astropy.modeling}
package provides tools to turn a simple function into a full-featured model,
but it also allows extending the built-in model class with arbitrary code.
